Bee visitation, pollination service, and plant yield in commodity and hybrid seed canola

### 2023-01-25 Manuscript/manuscript_files/supplemental.tex
Finished revisions

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{both_beeInt_time.png}
    \caption[Visitation model intercepts over time]{HB and LCB visitation models used random intercepts to account for variation between fields as well as over time. There was little systematic variation in HB intercepts across time, or between commodity field locations (Grand Prairie and Lethbridge), but there was a slight systematic decrease in seed field LCB intercepts during 2015, indicating that visitation rates declined across the season (this was not seen during the 2016 field season).}
\end{figure}

@@

Pollen- and nectar-foraging honey bees had different patterns of side-working, both on commodity canola, and the male and female lines of seed canola.
Side-working was common in nectar foragers, but was more common in commodity canola (64\%) than in the male (36\%) or female bays (2.8\%) of seed canola, indicating that a large proportion of honey bees foraging on canola flowers may never come in contact with the stigmas.
Pollen foragers were almost uniformly top-foragers in both commodity and seed fields (Table \ref{tab:sideWorking}), and pollen foragers were much less common in the female bays (1.4\%) than in the male bays (15\%), or in commodity fields (18\%).
Therefore, foraging honey bees in seed canola fields tend to treat male-fertile flowers similar to commodity canola flowers, but seem to top-work flowers more in commodity canola than seed fields.
Leafcutting bee foraging behaviours were not recorded, but anecdoctally, most seemed to almost exclusively top-work flowers in seed canola fields.

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{both_beeInt_time.png}
    \caption[Visitation model intercepts over time]{HB and LCB visitation models used random intercepts to account for variation between fields as well as over time. There was little systematic variation in HB intercepts across time, or between commodity field locations (Beaverlodge and Lethbridge), but there was a slight systematic decrease in seed field LCB intercepts during 2015, indicating that visitation rates declined across the season (this was not seen during the 2016 field season).}
\end{figure}

@@

Pollen- and nectar-foraging honey bees had different patterns of side-working, both on commodity canola, and the male and female bays of seed canola (Table S3).
Side-working was common in nectar foragers, but was more common in commodity canola (64\%) than in the male (36\%) or female bays (2.8\%) of seed canola, indicating that a large proportion of honey bees foraging on canola flowers may never come in contact with the stigmas.
Pollen foragers were almost uniformly top-foragers in both commodity and seed fields, and pollen foragers were much less common in the female bays (1.4\%) than in the male bays (15\%), or in commodity fields (18\%).
Therefore, foraging honey bees in seed canola fields tend to treat male-fertile flowers similar to commodity canola flowers, but seem to top-work flowers more in commodity canola than seed fields.
Leafcutting bee foraging behaviours were not recorded, but anecdoctally, most seemed to almost exclusively top-work flowers in seed canola fields.
